---
title: "Lab 1: Introduction to Quarto"
author: "Zack Kramer"
date: "9/26/24"
format: html
editor: source
embed-resources: true
execute:
  echo: false
  output: true
  error: true
---

# Part Two: Exploring Quarto Documents

## Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be
displayed. This [guide](https://quarto.org/docs/computations/execution-options.html)
provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML. 

**Question 2** -- Add an `execute` line to your YAML that includes the following
options, (1) your source code is always output on the page, and (2) your
document will render even if there are errors.

## Tooth Growth Dataset

```{r}
#| eval: false
#| echo: true
#| label: practicing-running-code

# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)

```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code
chunk and paste in the code provided in the Lab 1 instructions. 

### Check the Data Documentation

**Question 4** -- In your **console** (*not* in the Quarto document), type
`?ToothGrowth` (or alternatively `help(ToothGrowth)`.Use the information that
pops up in the *Help* pane in RStudio to fill in the blanks below. 

*This dataset investigates the effect of odontoblasts on tooth growth in guinea pigs*

*The two supplement delivery methods include OJ (orange juice) and VC (vitamin C).*

*`ToothGrowth` is a data frame with 60 observations and 3 variables.*

**Question 5** -- *Before* the code chunk, change the "Running the Provided
Code" section header to a header that better describes the contents of this
section (e.g., Tooth Growth Dataset).

## Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-align: "center"
#| fig-cap: 
#|   - "Box Plot 1"
#|   - "Box Plot 2"

library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")
```

Now, run this code chunk! You should see two side-by-side boxplots, one plot
comparing tooth length between the two supplement delivery methods and one plot
comparing tooth length between the three different dosages uses. 

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations)
and add an option (`#|`) to the above code chunk to make the figures print
side-by-side (i.e., in one row) in the rendered HTML file. 

**Question 8** -- Specify in the code chunk options that these boxplots 
should be **center aligned**.

**Question 9** -- Specify a **figure caption** for the boxplots (using a
code-chunk option).

## Two-sided t-test

```{r}
t.test(len ~ supp, data = ToothGrowth, var.equal = FALSE)
```
1. Using a traditional p-value of 0.05, we reject the null hypothesis, and conclude there is no significant difference between groups. 
2. There is 95% confidence that the true difference in average tooth length for the two supplements is between 0 and 7.6mm
